\section{Course Content}

\subsection{Overview of \acrfull{iot} \hfill { 4 Hrs.}}

\begin{enumerate}
    \item Definition of \acrfull*{iot}
    \item Trends of \acrshort*{iot}: History and Growth of the \acrshort*{iot} industry. Industries being powered by \acrshort{iot}.
    \item Fundamental components of \acrshort{iot} system
    \item Applications of \acrshort{iot}
\end{enumerate}

\subsection{Sensors and Devices used in \acrshort*{iot} \hfill {6 Hrs.}}

\begin{enumerate}
    \item Overview of Sensors and Devices.
    \item \acrfull*{iot} Device Hardware
    \item Scaling, Manufacturing and Shipping.
    \item Gateways
    
\end{enumerate}

\subsection{Connectivity \hfill {4 Hrs.}}

\begin{enumerate}
    \item Introduction to Connectivity.
    \item Cellular connectivity for \acrshort{iot}.
    \item Satellite connectivity for \acrshort{iot}.
    \item WiFi/Bluetooth/LPWAN connectivity for \acrshort{iot}.
    
\end{enumerate}

\subsection{Data Processing \hfill {4 Hrs.}}
\begin{enumerate}
    \item Introduction to the Cloud.
    \item Introduction to \acrfull{iot} Platform.
    \begin{itemize}
        \item Organization Strategies to choose an \acrshort{iot} platform.
        \item Types of \acrfull{iot} Platform
        \item Needs to migrate to an \acrfull{iot} Platform.
    \end{itemize}
    \item EDGE Computing and FOG Computing
    \item APIs to integrate \acrshort{iot} to custom application.
    
\end{enumerate}

\subsection{\acrshort{iot} Protocols and Machine Learning \hfill {9 Hrs.}}
\begin{enumerate}
    \item Overview of \acrshort{iot} Protocols.
    \item \acrfull{iot} Protocols: Data Protocols 
    \begin{itemize}
        \item MQTT
        \item CoAP
        \item AMQP
        \item M2M Communication Protocol
        \item XMPP
    \end{itemize}
    \item \acrfull{iot} Protocols: Network Protocols 
    \begin{itemize}
        \item HTTP
        \item LoRaWAN
        \item Bluetooth
        \item ZigBee
    \end{itemize}
    \item Machine Learning for \acrshort{iot}
\end{enumerate}

\subsection{User Interface and User Experience in \acrshort{iot} \hfill{2 Hrs.}}
\begin{enumerate}
    \item Introduction to UI/UX for \acrshort{iot}
    \item Key considerations for UI/UX.
    \item Recent trends in designing UI/UX for \acrshort{iot}.
\end{enumerate}

\subsection{Security and Privacy in \acrshort*{iot} \hfill{4 Hrs.}}
\begin{enumerate}
    \item IoT security challenges and threats
    \item Authentication and access control in IoT systems
    \item Data privacy and compliance in smart cities
    \item Security best practices for IoT deployments
\end{enumerate}

\subsection{\acrshort{iot} for Smart Cities \hfill{3 Hrs.}}
\begin{enumerate}
    \item Introduction to smart city.
    \item Needs for smart cities transformation.
    \item Roles of \acrfull{iot} in Smart Cities.
    \item Case Studies of Smart City.
\end{enumerate}

\subsection{Other technologies in Smart City \hfill {3 Hrs.}}
\begin{enumerate}
    \item \acrfull{bim} and \acrfull{gis} value for smart cities.
    \begin{itemize}
        \item BIM Dimensions
        \item Sustainability and Facility Management in BIM
        \item BIM Lifecycle
        \item Integrating BIM and GIS
    \end{itemize}
    \item Big Data
    \item Case Study: Applications of Smart City.
\end{enumerate}

\subsection{Smart City Design \hfill{6 Hrs.}}
\begin{enumerate}
    \item Smart energy management and grid systems
    \item Smart transportation and traffic management
    \item Environmental monitoring and sustainability
    \item Smart buildings and infrastructure
    \item Citizen participation in smart city initiatives
\end{enumerate}