\section*{Course Description}

% SEO stands for Search Engine Optimization. SEO is the process of improving the quality and quantity of website traffic to a website and a web page's ranking on search engines such as Google and Bing.

\bigskip The Internet of things (IoT) is a term for the growing number of electronics that aren't traditional computing devices, but are connected to the internet to send data, receive instructions or both.

\bigskip There's an incredibly broad range of things that fall under that umbrella: Internet-connected smart versions of traditional appliances like refrigerators and light bulbs, gadgets that could only exist in an internet-enabled world like Alexa-style digital assistants; internet-enabled sensors that are transforming factories, healthcare, transportation, distribution centers and farms.

\bigskip The IoT brings the power of the internet, data processing and analytics to the real world of physical objects. For consumers, this means interacting with the global information network without the intermediary of a keyboard and screen; many of their everyday objects and appliances can take instructions from that network with minimal human intervention.

\bigskip The IoT has an important application in smart cities. Smart City is about urban infrastructure management using smart devices. This course will enable the readers to realize the smart-city concepts. In addition to IOT, the readers will understand about the smart-city technologies like Building Information Modeling(BIM), Geographical Information System (GIS) and Artificial Intelligence(AI).