\section{Course Content}
\noindent
\subsection{Introduction \hfill (3 Hrs)} 

\begin{enumerate}
    \item Introduction to DevOps: Definition, Scope, Application.
    \item Introduction to Continuous Integration(CI) and Continuous Delivery(CD).
    \item Prerequisites Info and Setup: Chocolatey (Windows), Homebrew(MacOS), AWS Setup, Linux Setup. Server Management in Linux. 
    \item Basics of Networking
\end{enumerate}

\subsection{DevOps Basics with Virtualization \hfill (5 Hrs)} 

\begin{enumerate}
    \item Basics of Virtualization: Definition, Types and Heirarchy of Virtualizations.
    \item Learn Virtualization: Manual and Automatic. OS Environments: Linux, MacOS, and Windows
    \item Bash Scripting. Basics of Scripting.
    \item Variables, Conditons, Loops etc. 
    \item Automating day to day Admin Tasks.
    
\end{enumerate}

\subsection{V \hfill (6 hrs)} 

\begin{enumerate}
    \item Basic webpage designing. Key differences/similarities between a human visitor and search engine visitor. Website core structure.
    \item Tools for SEO Monitoring: Google Analytics, Bing Webmaster, Yandex Webmaster. 
    \item Different Frameworks available for SEO in popular programming languages like python, java, R etc.
    
\end{enumerate}

\subsection{Components of SEO \hfill (5 Hrs.)} 
\begin{enumerate}
    \item On-page SEO: On-page on-site SEO factors, Google Search Console, Yahoo \& Bing Webmaster tools. 
    \item Off-Page SEO: Off Page Activities, Introduction to Off-page optimization, Guest Article Posts. Off Page Tools: Business Listings.
    \item Site Optimization Techniques: Title tags, Meta tags, Header tags optimization.
    
\end{enumerate}


\subsection{Digital Marketing \hfill (5 Hrs.)}
\begin{enumerate}
    \item Introduction to Marketing. Online Vs. Offline Marketing. Mediums for Digital Marketing: Voice, Visuals, Text, Animation.
    \item Landscape of Digital Marketing. Target Audience. Strategies of Digital Marketing.
    \item Key Metrics for Measuring Success.
\end{enumerate}

\subsection{Content Marketing \hfill (9 Hrs.)}

\begin{enumerate}
    \item Introduction to Ontology. Use of OWL files like schema.org for site indexing.
    \item Understanding User Experience and User Interface Design.
    \item Website optimization for different devices.
    \item Planning for content Marketing
\end{enumerate}

\subsection{Social Media Marketing \hfill (4 Hrs.)} 
\begin{enumerate}
    \item Introduction to Social Media. Attributes of Engaging Content. Digital Actions for Social Media Campaigns.
    \item Opportunities of different social media for digital marketing: Facebook - page, group, marketplace etc. Twitter. LinkedIn.
    \item SEO efficiency with social media.
\end{enumerate}

\subsection{Advertising \hfill (3 Hrs.)}
\begin{enumerate}
    \item Paid Advertising: Introduction and Types.
    \item Campaigns for Advertisement: Creating and Managing PPC(Pay Per Click) Campaigns, Analytics and Reporting, Analyzing and Reporting on Digital Marketing Campaigns
\end{enumerate}

\subsection{Summing Up \hfill (5 Hrs.)}
\begin{enumerate}
    \item Ethical Considerations for Marketing: Ads Writing, WordStream, Copywriting
    \item Product Management with different marketing campaigns: Paper, Online, Digital etc.
    \item Emails and Newsletters in Digital Marketing.
    \item Content Design using AI tools for Digital Marketing and SEO.
\end{enumerate}